### 2014-11-08 heat-transfer.tex
Further updates.

In the Heat Transfer algorithm~(HT), we have a graph where heat values are
exchanged between nodes. The goal of the program is to exchange heat between
nodes. The program stops when the new heat values of every node are
$\delta = |H_i - H_{i-1}| \le \epsilon$. The algorithm works
asynchronously since heat values can be updated by using new partial information
coming from neighbor nodes. This increases parallelism since nodes do not need
to synchronize between iterations.

@@

To further improve locality, we split the second rule to
not send small $\delta$ values if the target node is in another
thread. XXX talk about results

@@

\begin{topfig}
   \begin{center}
      \subfloat[]{\includegraphics[width=5cm]{results/new-heat-transfer-80}}
   \end{center}
   \scap{results:ht}{Experimental results for the HT program. The coordinated version
      is, on average, 30\% faster than the regular version although it has a
      slightly worse scalability due to a reduction in work available.}
\end{topfig}

>>>>

In the Heat Transfer algorithm~(HT), we have a graph where heat values are
exchanged between nodes. XXX rewrite The program stops when the new heat values of every node are
$\delta = |H_i - H_{i-1}| \le \epsilon$. The algorithm works
asynchronously since heat values can be updated by using new partial information
coming from neighbor nodes. This increases parallelism since nodes do not need
to synchronize between iterations.

@@

To further improve locality, we split the second rule to
not send small $\delta$ values if the target node is in another
thread (Fig.~\ref{code:ht_better}). The \textbf{Local-Only} line in
Fig.~\ref{results:ht} shows that improving locality by disabling small updates
improves the execution time of HT. XXX update figure

@@

\begin{topfig}
   \begin{center}
      \subfloat[]{\includegraphics[width=5.5cm]{results/new-heat-transfer-80}}
   \end{center}
   \scap{results:ht}{Experimental results for the HT program. The coordinated version
      is, on average, 30\% faster than the regular version although it has a
      slightly worse scalability due to a reduction in work available.}
\end{topfig}

### 2014-11-08 implementation.tex
use new scap and fig macros
Further updates.

\begin{figure}[h!]
   \centering
   \includegraphics[width=0.4\textwidth]{node_states.pdf}
   \caption{The node state machine as represented by the state variable. During
      the lifetime of a program, each node goes through different states as
      specified by the state machine.}
   \label{fig:node_states}
\end{figure}

@@

Threads pop active nodes from a thread local queue and execute new candidate rules to
generate new facts, which in turn can activate other nodes.
In order to reduce inter-thread communication, node priorities are implemented
at the thread level. This means that, when a thread picks the highest
priority node, it is actually the highest priority from the set of nodes owned
by the thread and not the highest priority node in the whole program.
To allow node priorities, we use 2 two pairs of queues per thread: a pair of doubly linked
lists known as the \emph{standard queue} and a pair of min/max heap known as the \emph{priority queue}.

@@

\begin{figure}[h!]
   \begin{center}
      \subfloat[]{\includegraphics[width=8cm]{results/comparison1.png}}
   \end{center}
   \caption{Measuring the overhead of coordination mechanisms. The \textbf{Old}
   bars represent the performance of the original virtual machine, while
   \textbf{New} is the relative performance of the new version that includes
   coordination mechanisms.}
   \label{results:comparison1}
\end{figure}

>>>>

\begin{topfig}
   \centering
   \includegraphics[width=0.4\textwidth]{node_states.pdf}
   \scap{fig:node_states}{The node state machine as represented by the state variable. During
      the lifetime of a program, each node goes through different states as
      specified by the state machine.}
\end{topfig}

@@

Threads pop active nodes from a thread local queue and execute new candidate rules to
generate new facts, which in turn can activate other nodes.
XXX NEEDS REWRITE
In order to reduce inter-thread communication, node priorities are implemented
at the thread level. This means that, when a thread picks the highest
priority node, it is actually the highest priority from the set of nodes owned
by the thread and not the highest priority node in the whole program.
To allow node priorities, we use 2 two pairs of queues per thread: a pair of doubly linked
lists known as the \emph{standard queue} and a pair of min/max heap known as the \emph{priority queue}.

@@

\begin{topfig}
   \begin{center}
      \subfloat[]{\includegraphics[width=8cm]{results/comparison1.png}}
   \end{center}
   \scap{results:comparison1}{Measuring the overhead of coordination mechanisms. The \textbf{Old}
   bars represent the performance of the original virtual machine, while
   \textbf{New} is the relative performance of the new version that includes
   coordination mechanisms.}
\end{topfig}

### 2014-11-08 splash-bp.tex
Further updates.

\begin{dblfig}
   \begin{center}
      \subfloat[]{\includegraphics[width=5cm]{results/system_belief-propagation-400.png}}
      \subfloat[]{\includegraphics[width=5cm]{results/system_splash-bp-400.png}}
      \subfloat[]{\includegraphics[width=5cm]{results/system_improve_belief-propagation-400.png}}
   \end{center}
   \scap{results:splash_bp}{Experimental results for LBP and SBP. Figure (a) shows the
      scalability of LBP for both CLM and GraphLab and Figure (b) shows the
      scalability of SBP. Figure (c) presents the
      improvements seen in SBP against LBP, where SBP runs, on average, 1.5 to 2.5
      times faster than LBP.}
\end{dblfig}

>>>>

\begin{dblfig}
   \begin{center}
      \subfloat[]{\includegraphics[width=5.5cm]{results/system_belief-propagation-400.png}}
      \subfloat[]{\includegraphics[width=5.5cm]{results/system_splash-bp-400.png}}
      \subfloat[]{\includegraphics[width=5.5cm]{results/system_improve_belief-propagation-400.png}}
   \end{center}
   \scap{results:splash_bp}{Experimental results for LBP and SBP. Figure (a) shows the
      scalability of LBP for both CLM and GraphLab and Figure (b) shows the
      scalability of SBP. Figure (c) presents the
      improvements seen in SBP against LBP, where SBP runs, on average, 1.5 to 2.5
      times faster than LBP.}
\end{dblfig}
